Bayesian MCMC diagnostics and summarisation using Tracer 1.6

### 2017-08-03 manuscript/tracer16.tex
update acknowledgments

We thank the National Evolutionary Synthesis Center (NESCent) for sponsoring a working group (Software for Bayesian Evolutionary Analysis) that facilitated the development of Tracer version 1.6. 
This work was supported in part by funding from the Marsden Trust, NSF (DMS 0856099), NIH (R01 GM086887, R01 HG006139), The Royal Society of London, BBSRC (BB/H011285/1) and the Wellcome Trust (WT092807MA).

>>>>

This work was supported in part by
the Wellcome Trust through project 206298/Z/17/Z (Artic Network),
the European Union Seventh Framework Programme under grant agreement no. 725422-RESERVOIRDOCS,
the National Science Foundation through grant DMS 1264153,
the National Institutes of Health under grant R01 AI107034,
and
the Marsden Trust.
